\chapter{Product Functions} \label{ch:product_functions}

\section{Implemented Functions}

All the requirements that are satisfied with the initial prototype of the program are listed below. \todo{Add justification}

\begin{longtable}{@{}p{0.06\linewidth} p{0.88\linewidth}}
	\toprule
	\textbf{ID}   & \textbf{Requirement}\\
	\midrule
	
	& \textbf{Authentication}\\
    \midrule
	\textbf{R1.} & The system must uniquely identify each user by his e-mail. \\
	\textbf{R2.} & The system must allow an unregistered user to create an account with a chosen role. \\
	\textbf{R4.} & The system must ensure that a farmer inserts his farm data during the registration process.\\
	\textbf{R6.} & The system must allow a registered user to log in to the application. \\
	\textbf{R7.} & The system must allow a registered user to reset his password. \\
	\textbf{R8.} & The system must allow a logged-in user to sign out of the application. \\
	\textbf{R9.} & The system must allow a registered user to delete his account. \\
    \midrule

	& \textbf{Policy maker} \\
    \midrule
	\textbf{R10.} & The system must allow a policy maker to assign a note to a farmer.\\
	\textbf{R11.} & The system must ensure that every farmer initially has a neutral note.\\
	\textbf{R12.} & The system must have a list of predefined farmer's problem types.\\
    \textbf{R13.} & The system must allow a policy maker to specify a problem type when assigning a negative note.\\
	\textbf{R17.} & The system must ensure that an automatic help request followed by additional farm visits are created, if a farmer receives a negative note.\\
	& \textit{\textbf{R17} is implemented only partially - without creating additional farm visits.}\\
	\textbf{R19.} & The system must allow a policy maker to see a list of all farmers in Telangana.\\
	\textbf{R20.} & The system must allow a policy maker to see a list of all farmers with a specific note.\\
	\textbf{R21.} & The system must allow a policy maker to see a list of all farmers in a given mandal.\\
	\textbf{R22.} & The system must allow a policy maker to find a farmer's summary by his name and surname.\\
	\textbf{R23.} & The system must allow a policy maker to see a farmer's summary.\\
	\midrule

    & \textbf{Farmer}\\
    \midrule
	\textbf{R24.} & The system must allow a farmer to see his own farmer's summary.\\
	\textbf{R25.} & The system must allow a farmer to see personalized suggestions.\\
	\textbf{R26.} & The system must allow a farmer to manage his monthly production data.\\
	\textbf{R27.} & The system must allow a farmer to see a list of help requests created by him.\\
	\textbf{R28.} & The system must allow a farmer to find a help request created by him by the topic.\\
	\textbf{R29.} & The system must allow a farmer to see a specific help request created by him.\\
	\textbf{R30.} & The system must allow a farmer to delete a specific help request created by him.\\
	\textbf{R31.} & The system must allow a farmer to create a new help request.\\
	\textbf{R32.} & The system must allow a farmer with a positive note to see a list of all help requests in his mandal.\\
	\textbf{R33.} & The system must allow a farmer with a positive note to find a help request in his mandal by the topic.\\
	\textbf{R34.} & The system must allow a farmer with a positive note to see a specific help request in his mandal.\\
	\textbf{R35.} & The system must allow a farmer with a positive note to respond to a specific help request in his mandal.\\
	\textbf{R36.} & The system must allow a farmer with a positive note to delete a help response, only if it was created by him.\\
	\textbf{R37.} & The farmer is able to see farmer's summary of a farmer with a negative note whose help request he received. \\
	\textbf{R38.} & The system must allow a farmer to see a list of all forum threads in Telangana.\\
	\textbf{R39.} & The system must allow a farmer to find a forum thread by the topic.\\
	\textbf{R40.} & The system must allow a farmer to see a specific forum thread with its comments.\\
	\textbf{R41.} & The system must allow a farmer to create a comment in a forum thread.\\
	\textbf{R42.} & The system must allow a farmer to delete a comment in a forum thread, only if it was created by him.\\
	\textbf{R43.} & The system must allow a farmer to create a forum thread.\\
	\midrule

    & \textbf{External systems}\todo{Decide on the implementation}\\
    \midrule
	\textbf{R65.} & The system must read and update weather forecasts every day. \\
	\textbf{R66.} & The system must read and store data from humidity sensors every day. \\
	\textbf{R67.} & The system must read and store data from water irrigation systems every day. \\
	\textbf{R68.} & The system must ensure that a farmer who creates a help request cannot be its recipient.\\
		
	\bottomrule
\end{longtable}

\section{Excluded Functions}

\begin{longtable}{@{}p{0.06\linewidth} p{0.88\linewidth}}
	\toprule
	\textbf{ID}   & \textbf{Requirement}\\
	\midrule
	
	%Authentication
	\textbf{R3.} & The system must ensure that an agronomist chooses the area of responsibility during the registration process. \\
	\textbf{R5.} & The system must ensure that two casual farm visits are scheduled for each year of the farm's existence.\\
	
	%Policy maker
    \textbf{R14.} & The system must ensure that a farm is visited more often in the event of any problems.\\
    \textbf{R15.} & The system must have a specified number of additional visits caused by each predefined problem type.\\
    \textbf{R16.} & The system must ensure that only the most recently specified problem type is taken into account when determining the number of visits.\\
	\textbf{R18.} & The system must ensure that all the additional farm visits created due to obtaining a negative note are deleted after a farmer's negative note is updated with a positive or a neutral one.\\
	
	%Agronomist
	\textbf{R44.} & The system must allow an agronomist to manage his area of responsibility.\\
	\textbf{R45.} & The system must allow an agronomist to see the list of suggestions for mandals in his area of responsibility.\\
	\textbf{R46.} & The system must allow an agronomist to manage the list of suggestions for mandals in his area of responsibility.\\
	\textbf{R47.} & The system must allow an agronomist to see a list of all farmers in his area of responsibility.\\
	\textbf{R48.} & The system must allow an agronomist to see a list of all farmers with a specific note in his area of responsibility.\\
	\textbf{R49.} & The system must allow an agronomist to see a list of all farmers in a given mandal in his area of responsibility.\\
	\textbf{R50.} & The system must allow an agronomist to find a farmer's summary in his area of responsibility by his name and surname.\\
	\textbf{R51.} & The system must allow an agronomist to see a farmer's summary in his area of responsibility.\\
	\textbf{R52.} & The system must allow an agronomist to see a list of all help requests in his area of responsibility.\\
	\textbf{R53.} & The system must allow an agronomist to find a help request in his area of responsibility by the topic.\\
	\textbf{R54.} & The system must allow an agronomist to see a specific help request in his area of responsibility.\\
	\textbf{R55.} & The system must allow an agronomist to respond to a specific help request in his area of responsibility.\\
	\textbf{R56.} & The system must allow an agronomist to delete a help response, only if it was created by him.\\
	\textbf{R57.} & The system must allow an agronomist to see his daily plans.\\
	\textbf{R58.} & The system must allow an agronomist to submit a daily plan's execution state, by rejecting or confirming each visit, on the same date or after the daily plan's date has passed. \\
	\textbf{R59.} & The system must allow an agronomist to provide a comment for a visit he is confirming.\\
	\textbf{R60.} & The system must ensure that after an agronomist submits his daily plan, for all the causal visits marked as confirmed, new ones are created in approximately half of a year.\\
	\textbf{R61.} & The system must allow an agronomist to delete a visit before its date.\\
	\textbf{R62.} & The system must ensure that a deleted visit is marked as rejected.\\
	\textbf{R63.} & The system must ensure that in case of rejecting a casual visit, a new one is created in maximally 5 days.\\
	\textbf{R64.} & The system must allow replanning any different visit than a casual one without any constraints.\\
		
	\bottomrule
\end{longtable}
