\chapter{Introduction}

\section{Purpose}

% TODO: To introduce some background based on the Context.

% rising food demand
% climate change
% covid19 pandemic

Over 58 percent of rural Indian households rely on agriculture as their primary source of income, with 80 percent of them being smallholder farmers with less than 2 hectares of land. Furthermore, more than 20 percent of smallholder agricultural households live in poverty. Food consumption is anticipated to climb by 59 percent to 98 percent by 2050, according to the Harvard Business Review \cite{global_demand_for_food}.

With climate change posing a serious danger to agriculture, a complete overhaul of the system that transports food from farmers to our tables is required. On the top of that, the coronavirus pandemic created a huge disruption in food supply chains, exposing the weak parts of small-scale farmers as well as the significance of constructing resilient food systems.

Telangana is India's 11th biggest state, having a land area of 122,077$km^2$ and a population of 35,193,978 people (data from 2011) \cite{telangana}. The project's goal is to help Telangana’s government promote data-driven policy-making in the state by designing, developing, and demonstrating anticipatory governance models for food systems utilizing digital public goods and community-centric approaches \cite{reference_doc}.

\subsection{Goals} \label{subsec:goals}
\begin{itemize}
	\item [\textbf{G1.}] Improve farmers performance by providing them with personalized suggestions.
	\item [\textbf{G2.}] Acquire, combine, and visualize data from external systems. 
	\item [\textbf{G3.}] Facilitate performance assessment of the farmers.
	\item [\textbf{G4.}] Promote regular farms' visits by agronomists, depending on the type of problems they face.
	\item [\textbf{G5.}] Enable agronomists to exchange information with farmers.
	\item [\textbf{G6.}] Enable farmers to exchange their knowledge.
\end{itemize}

\section{Scope}

Data dRiven PrEdictive FArMing (DREAM) is a project that intends to redesign the food production process in the Telangana area in order to create more resilient agricultural systems that will be required to meet the region's rising food demand. To address such a broad issue, it is critical to bring together individuals from many professions and backgrounds; hence, the participation of groups such as stakeholders, policy makers, farmers, analysts, and agronomists is desirable.

Data acquisition and combination can be viewed as the first feasible step in achieving the goal. This information might be gathered from farmers, specialized sensors installed on the ground that detect soil humidity, and government agronomists who visit fields on a regular basis.

The system aims to enable policy makers to identify farmers who perform well, especially under tough weather conditions, farmers who perform particularly badly and require assistance, and understand if agronomist-led steering initiatives yield substantial outcomes. This is going to be achieved by continuous assessment based on the visualizations of the acquired data.

Another group that would benefit from the system are the farmers, since it will allow them to exchange good practices between each other and request help when needed. All of that will be supplemented with visualizations of relevant data, including suggestions and weather forecasts.

The project also intends to facilitate the work of agronomists by creating a daily plan for field visits, giving statistics on farmers' performance, and informing them about incoming assistance requests.

The system attempts to address a highly difficult topic, which necessitates the coordination of numerous individuals. All of these criteria requires the system to be very easy to use, intuitive, and straightforward, so that everyone can get the most out of it.

\subsection{World Phenomena}

\begin{longtable}{@{}p{0.06\linewidth} p{0.90\linewidth}@{}}
	\toprule
	\textbf{ID}   & \textbf{Phenomena}\\
	\midrule
	\autonum{WP} & Telangana's government collects information concerning short-term and long-term meteorological forecasts \cite{tsdps}.\\
	\autonum{WP} & Water irrigation systems collect information about the amount of water used by each farm.\\
	\autonum{WP} & Sensors collect information about the humidity of the soil at a given farm.\\
	\autonum{WP} & An agronomist visits a farm.\\
	\autonum{WP} & A farmer produces crops on his farm.\\
	\autonum{WP} & A farmer experiences issues on his farm.\\
	\autonum{WP} & A user forgets his password.\\
	\autonum{WP} & An external company provides a farm with a water irrigation system.\\
	\autonum{WP} & An external company provides a farm with a sensor system.\\
	
	\bottomrule
\end{longtable}

\subsection{Shared Phenomena}

\begin{longtable}{@{}p{0.06\linewidth} p{0.66\linewidth} p{0.20\linewidth}@{}}
	\toprule
	\textbf{ID}  & \textbf{Content} & \textbf{Controlled by}\\
	\midrule
	
	% Unregistered user
    \textbf{SP1.} & A user logs into the system. & World \\
    \textbf{SP2.} & An unregistered user creates an account in the system. & World \\
    \textbf{SP3.} & The system creates an instance of a farm during a registration process of a farmer. & Machine \\
    
    %System
    \textbf{SP4.} & The system reads and stores information about short-term and long-term meteorological forecasts provided by the API of Telangana's government. & Machine \\
    \textbf{SP5.} & The system reads and stores information about the amount of water used by each farm, provided by the water irrigation system's API. & Machine \\
    \textbf{SP6.} & The system reads and stores the data collected by the sensors at a given farm, provided by the sensor system's API. & Machine \\
    \textbf{SP7.} & The system sends a request for help to well performing farmers and agronomists in a given mandal.  & Machine \\
    
    %All
    \textbf{SP8.} & The system shows a filterable list of farmers. & Machine \\
    \textbf{SP9.} & The system shows farmer's summary. & Machine \\
    \textbf{SP10.} & A user requests password reset. & World\\
    \textbf{SP11.} & The system sends an email with password reset link. & Machine \\
    \textbf{SP12.} & A user resets the password using a link obtained in an email. & World \\
    \textbf{SP13.} & A registered user deletes his account. & World \\
    
    %Farmer
    \textbf{SP14.} & A farmer manages his production data in the system. & World \\
    \textbf{SP15.} & A farmer requests for help in the system. & World \\
    \textbf{SP16.} & A farmer deletes his help request in the system. & World \\
    \textbf{SP17.} & A farmer with a positive note responds to a request for help in the system. & World \\
    \textbf{SP18.} & A farmer with a positive note deletes his help response in the system. & World \\
    \textbf{SP19.} & A farmer sees a list of all the forum threads. & World\\
    \textbf{SP20.} & A farmer reads a forum thread. & World\\
    \textbf{SP21.} & A farmer creates a thread on the forum.  & World \\
    \textbf{SP22.} & A farmer removes his thread from the forum.  & World \\
    \textbf{SP23.} & A farmer comments in a given thread. & World \\
    \textbf{SP24.} & A farmer removes his comment from a given thread. & World \\
    
    %Agronomist
    \textbf{SP25.} & An agronomist saves comments collected during a farm visit in the system. & World \\
    \textbf{SP26.} & The agronomist inserts into the system personalized suggestions for the farmers inside his area of responsibility. & World \\
    \textbf{SP27.} & An agronomist responds to a request for help in the system. & World \\
    \textbf{SP28.} & An agronomist deletes a help response in the system. & World \\
    \textbf{SP29.} & An agronomist manages his area of responsibility. & World \\
    \textbf{SP30.} & The system visualizes data about farmers with a specific note in the agronomist's area of responsibility. & Machine \\
    \textbf{SP31.} & The system shows the daily plan of an agronomist. & Machine \\
    \textbf{SP32.} & An agronomist manages the daily plan. & World \\
    \textbf{SP33.} & An agronomist submits the execution state of the daily plan. & World \\
    \textbf{SP34.} & The system generates farm visits for an agronomist in a given area of responsibility. & Machine \\
    
    %Policy maker
    \textbf{SP35.} & A policy maker assesses a farmer's performance, giving him a negative, neutral or positive note and saves it in the system. & World \\
    \textbf{SP36.} & A policy maker understands whether activities performed by agronomists and farmers helped a farmer with a negative note based on the data from the system. & World \\
    
	\bottomrule
\end{longtable}

\section{Definitions, Acronyms, Abbreviations}

\subsection{Definitions}

\begin{center}
\begin{longtable}{@{}p{0.28\linewidth} p{0.68\linewidth}@{}}
		\toprule
		\textbf{Expression}     & \textbf{Definition}\\
		\midrule
% 		Water irrigation system - system urzadzen na farmie
% 		Sensor - urzadzenie na farmie
% 		Sensor system - system urzadzen na farmie
% 		Water irrigation system's ID - ID systemu urzadzen na farmie
% 		Sensor system's ID - ID systemu urzadzen na farmie
% 		External data providers
		Water irrigation system & Collection of external devices which gather information about the amount of water used on a given farm. Collected data are available via an API. \\
        Sensor/Humidity sensor & External device which collects information about the humidity of soil on a given farm.\\
        Sensor system           & Collection of all the sensors on a farm. Collected data are available via an API.\\
        Farmer's summary        & Summary of farmer and farm data. Contains: information about farmer and his farm, note history, short-term weather forecasts, production data, farm visits, weather forecast history, soil humidity data, water usage, and help requests.\\
        Farmer's note           & Evaluation note given by a governmental policy maker based on a farmer's performance. Can include a type of problem, that the farmer is facing. Can be negative, neutral, or positive.\\
        Farm data               & Data concerning a farm, inserted by a farmer during account creation. Consist of water irrigation system’s ID, sensor system’s ID and farm's address (address line 1, address line 2, postal code, city and mandal).\\
        Personalized suggestion & Suggestions proposed to the farmers, based on a mandal and types of production of a given farm. Suggestions are inserted into the system by agronomists.\\
        Production type         & Kind of plants being produced on Telangana's farms.\\
        Production data         & Information provided by a farmer about his production. It lists production types and quantities (in kg) generated per type.\\
        Mandal                  & A local government area in India. Part of a district, which in turn is a part of a state.\\
        Dashboard               & The first screen that appears to the user after logging in to the system.\\
        Area of responsibility  & Set of mandals that an agronomist is responsible for.\\
        Daily plan              & A daily schedule for visiting farms in a certain area of responsibility.\\
        Casual visit            & A visit automatically arranged by the system. There are two casual visits to each farm every year.\\
        Request for help, Help request & An issue created by a farmer. It contains a topic, description and a problem. The system automatically forwards it to well-performing farmers and agronomists in the same mandal.\\
        Peak hours              & 6 a.m. to 9 a.m., and 5 p.m. to 8 p.m. in the GMT+5:30 time zone.\\
        External systems        & Systems that are not a part of DREAM and collect various farm-specific data and share them via an API. Following external systems are used: Weather Forecast System, Water Irrigation System, Sensor System.\\
        Water irrigation system's ID    & Number which uniquely identifies a water irrigation system. It is necessary for definition of the external system's API endpoint. The number is provided during installation of the water irrigation system.  \\
        Sensor system's ID              & Number which uniquely identifies a sensor system. It is necessary for definition of the external system's API endpoint. The number is provided during installation of the sensor system. \\
	\end{longtable}
\end{center}

\subsection{Acronyms}

\begin{center}
	\begin{longtable}{@{}p{0.28\linewidth} p{0.68\linewidth}@{}}
		\toprule
		\textbf{Acronyms}   & \textbf{Expression}\\
		\midrule
		DREAM               & Data-dRiven PrEdictive FArMing in Telangana\\
		RASD                & Requirements Analysis and Specifications Document\\
		G                   & Goal\\
		WP                  & World Phenomena\\
		SP                  & Shared Phenomena\\
		R                   & Requirement\\
		A                   & Domain assumption\\
		API                 & Application Programming Interface\\
		PBKDF2              & Password-Based Key Derivation Function 2 \\ 
		HMACSHA1            & Hash-based Message Authentication Code (HMAC) using the SHA1 hash function \\
		\bottomrule
	\end{longtable}
\end{center}

\subsection{Abbreviations}

\begin{center}
	\begin{longtable}{@{}p{0.28\linewidth} p{0.68\linewidth}@{}}
		\toprule
		\textbf{Abbreviations}  & \textbf{Expression}\\
		\midrule
	    a.m. & ante meridiem\\
	    p.m. & post meridiem\\
	    e.g. & exempli gratia\\
		\bottomrule
	\end{longtable}
\end{center}

\section{Revision History}

\begin{center}
	\begin{longtable}{@{}p{0.18\linewidth} p{0.18\linewidth} p{0.57\linewidth}@{}}
		\toprule
		\textbf{Date}   & \textbf{Revision} & \textbf{Notes}\\
		\midrule
		\date{}         & v.1.0             & First release.\\
% 		\date{} & v.1.1 & \begin{itemize}[label={--},leftmargin=.4cm,noitemsep,topsep=0pt,before=\vspace{-3.5mm},after=\vspace{-4mm}]
% 			\item Change 1
% 			\item Change 2
% 		\end{itemize}\\
		\bottomrule
	\end{longtable}
\end{center}

\printbibliography[title={Reference Documents},keyword=intro, heading=subbibnumbered]

\section{Document Structure}

\begin{enumerate}
    \item \textbf{Introduction}: describes the general purpose of the project, as well as its scope. Furthermore, it defines specific definitions, acronyms, and abbreviations used throughout the document.
    \item \textbf{Overall Description}: provides a general description of the system, with the focus on its perspective, functions, characteristics, and assumptions.
    \item \textbf{Specific Requirements}: focuses on external interface, functional, and performance requirements. Design constraints and software system attributes are defined in this chapter. Specific use cases are depicted on \textit{UML} diagrams.
    \item \textbf{Formal Analysis using Alloy}: describes the formal modeling activity, and the model itself. Additionally, it provides verification of critical aspects of the system and an example of the generated world.
    \item \textbf{Effort Spent}: depicts information about the project contribution of each group member.
    \item \textbf{References}
\end{enumerate}
