\chapter{User Interface Design}

DREAM is a web-based application. It could be utilized on a variety of devices, independent of form factor. The application, however, is expected to be largely utilized on desktop computers. As a result, the mockups given in RASD depict representations of the application's desktop version.

This chapter provides a list of all the already presented mockups, that will be later used for the requirements traceability (see chapter \ref{ch:requirements_traceability}).

\subsubsection{Unregistered user}

\begin{itemize}
    \item \textbf{M1.} User registration.
    \item \textbf{M2.} Farmer registration.
    \item \textbf{M3.} Agronomist registration.
\end{itemize}

\subsubsection{Farmer}

\begin{itemize}
    \item \textbf{M4.1.} Farmer's user view - part 1.
    \item \textbf{M4.2.} Farmer's user view - part 2.
    \item \textbf{M5.} Farmer's dashboard.
    \item \textbf{M6.} Farmer's production data.
    \item \textbf{M7.} Help requests created by farmer.
    \item \textbf{M8.} Specific help request created by farmer.
    \item \textbf{M9.} Help requests received by farmer with positive note.
    \item \textbf{M10.} Specific help request received by farmer with positive note (applicable also for the agronomist).
    \item \textbf{M11.} Forum view.
    \item \textbf{M12.} Specific forum thread.
\end{itemize}

\subsubsection{Agronomist}

\begin{itemize}
    \item \textbf{M13.} Agronomist's user view.
    \item \textbf{M14.} Agronomist's dashboard.
    \item \textbf{M15.} List of farmers (applicable also for the policy maker).
    \item \textbf{M16.} Calendar of daily plans.
    \item \textbf{M17.} Submitting executions state of a daily plan.
    \item \textbf{M18.} Help requests received by agronomist.
    \item \textbf{M19.} Managing suggestions.
\end{itemize}

\subsubsection{Policy maker}

\begin{itemize}
    \item \textbf{M20.} Policy maker's user view.
    \item \textbf{M21.} Policy maker's dashboard.
    \item \textbf{M22.} Partial view of farmer's summary, with option to change note.
\end{itemize}